Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2017-01-31 Experiments.tex
Iteration organization

%\jhanote{Not sure this should be under ``PANDA:Future/ROAD MAP?'' (cut and paste error it was not meant to be; FIXED)}
\section{Experiments}
The execution of jobs on TITAN follows a three step scheme: i) as first, TITAN's Backfill queue communicates  the availability of a slot i.e. a set of idle cores for a given time period\aanote{How many offers does PanDA receive per time unit? Average nodes per offer?}; ii) then, PanDA can decide to run on the slot or wait until a larger slot becomes available; iii) if the slot is taken, PanDA wraps a certain amount of events in a job and sends the job for execution.\aanote{I am supposing that the concept of event has been already introduced at this point}.

@@

On one hand, this %\jhanote{I would use the word execution strategy carefully. Maybe a more general term such as execution model, a special type of which is execution strategy?(I Agree, FIXED)} 
execution model leads to a drastic reduction of the queue time and, consequently, it guarantees high-performances. On the other hand, this model is tailored for the execution of ATLAS workload on TITAN by using the Backfill queue\mtnote{Do we have a queue dedicated to backfilling on Titan or should we speak of backfilling done on one or more queues?}.

@@

For this reason, in the remaining of this section we propose experimental results to address them. The idea behind the experiments is to show the behaviour of ATLAS workload on TITAN's batch queue.

First, we investigate the acquisition of slot as a function of time (wall-time) and space (number of cores) in order to understand how TITAN's scheduler and workload behave under different slot requests. This analysis includes two bulks of experiments: the first, generated ``in silico'', is based on simulations of the TITAN's scheduler by means of the Moab simulator \cite{}, whereas the second, generated ``in vivo'',  considers real submissions of ATLAS workload on TITAN's batch queue.

@@

This execution model introduces slot utilization as one of the key factors for high-performances. This happens because, in order to minimize the time spent in queue, we might asks for slots in advance and, then we could not br able to saturate them when they become available. Thus, this strategy requires a new functionality that allows the job to receive and execute new events while it is already running on the resources.
In order to do that we perform the experiments by using a new generation executor that implements such functionality.

>>>>

%\jhanote{Not sure this should be under ``PANDA:Future/ROAD MAP?'' (cut and paste error it was not meant to be; FIXED)}

\subsection{Experiments}

The execution of jobs on TITAN follows a three step scheme: (i) as first,
TITAN's Backfill queue communicates  the availability of a slot i.e., a set of
idle cores for a given time period\aanote{How many offers does PanDA receive per
time unit? Average nodes per offer?}; (ii) then, PanDA can decide to run on the
slot or wait until a larger slot becomes available; (iii) if the slot is taken,
PanDA wraps a certain amount of events in a job and sends the job for
execution.\aanote{I am supposing that the concept of event has been already
introduced at this point}.

@@

On one hand, this
% \jhanote{I would use the word execution strategy carefully. Maybe a more
% general term such as execution model, a special type of which is execution
% strategy?(I Agree, FIXED)}
execution model leads to a drastic reduction of the queue time and,
consequently, it guarantees high-performances. On the other hand, this model is
tailored for the execution of ATLAS workload on TITAN by using the Backfill
queue\mtnote{Do we have a queue dedicated to backfilling on Titan or should we
speak of backfilling done on one or more queues?}.

@@

For this reason, in the remaining of this section we propose experimental
results to address them. The idea behind the experiments is to show the behavior
of ATLAS workload on TITAN's batch queue.

First, we investigate the acquisition of slot as a function of time (wall-time)
and space (number of cores) in order to understand how TITAN's scheduler and
workload behave under different slot requests. This analysis includes two bulks
of experiments: the first, generated ``in silico'', is based on simulations of
the TITAN's scheduler by means of the Moab simulator~\cite{}, whereas the
second, generated ``in vivo'',  considers real submissions of ATLAS workload on
TITAN's batch queue.

@@

This execution model introduces slot utilization as one of the key factors for
high-performances. This happens because, in order to minimize the time spent in
queue, we might asks for slots in advance and, then we could not be able to
saturate them when they become available. Thus, this strategy requires a new
functionality that allows the job to receive and execute new events while it is
already running on the resources. In order to do that we perform the experiments
by using a new generation executor that implements such functionality.
